---
title: "Mapping Boston Restaurants"
author: "Team: Ningze(Summer) ZU, Jing(Mira) Tang ,Xiang Xu Jianhao Yan "
date: "11/3/2018"
output:
  html_document:
  df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load("leaflet", "sp", "magrittr", "maps", "htmltools", "rgdal", "ggplot2", "maptools", "XML", "readr", "rgeos", "rmapshaper", "tidyverse", "lubridate", "ggmap", "ggrepel","RCurl", update = FALSE) 
```

```{r, warning = FALSE}
# Import data
mayorsfoodcourt <- read.csv("https://data.boston.gov/dataset/03693648-2c62-4a2c-a4ec-48de2ee14e18/resource/4582bec6-2b4f-4f9e-bc55-cbaa73117f4c/download/mayorsfoodcourt.csv", header=T)

# Data Cleaning
# filter food courts whose licsense status is active
mayorsfoodcourt %>%
  filter(LICSTATUS == "Active") %>%
  dplyr::select(businessName, LICSTATUS, ViolLevel, VIOLDTTM, Address, CITY, ZIP, Location) %>%
  separate(Location, c("lat", "long"), ",") -> foodcourt

# filter food courts whose licsense status is active and VIOLDTTM in 2018.
foodcourt_2018 <- mayorsfoodcourt %>%
  filter(str_detect(VIOLDTTM, "2018")) %>%
  filter(LICSTATUS == "Active") %>%
  separate(Location, c("lat", "long"), ",") %>%
filter(!is.na(long) & !is.na(lat))

# covert location into latitude and longtitude.
foodcourt$lat <- as.numeric(gsub("\\(", "", foodcourt$lat))
foodcourt$long <- as.numeric(gsub(")", "", foodcourt$long))
foodcourt_2018$lat <- as.numeric(gsub("\\(", "", foodcourt_2018$lat))
foodcourt_2018$long <- as.numeric(gsub(")", "", foodcourt_2018$long))

# create new variables indicate the violation times of each food court
count <- aggregate(data.frame(count = foodcourt_2018$businessName), list(value = foodcourt_2018$businessName), length)
foodcourt_2018 <- foodcourt_2018[!duplicated(foodcourt_2018$businessName), ]
foodcourt_2018 <- cbind(foodcourt_2018, count)
foodcourt %>% group_by(businessName, Address) %>% count() %>% arrange(desc(n)) -> food
colnames(food)[3] <- "VioCount"
foodcourt %>% dplyr::select(businessName, LICSTATUS, Address, CITY, ZIP, lat, long) -> location
location <- unique(location)

# how many NAs
sum(is.na(location$lat))
as.numeric(sum(is.na(location$lat)) / count(unique(location))) # location
print("There are 34% location in our data are missing.")

# create a dataset with count of violation times and the geographic info of foodcourts
food$ID <- paste(food$businessName, food$Address)
location$ID <- paste(location$businessName, location$Address)
food <- left_join(food, location, by = "ID")
food$businessName.y <- NULL
food$Address.y <- NULL
food$ID <- NULL
food$LICSTATUS <- NULL
colnames(food)[1] <- "businessName"
colnames(food)[2] <- "Address"
food <- na.omit(food)
```

## Top 10 Food Courts in MA with the Most Violations
```{r, warning = FALSE}
food.10 <- food[1:10,]
content <- paste(sep = "<br/>",
                 food.10$businessName,
                 food.10$Address,
                 food.10$CITY,
                 food.10$VioCount
)

Icon <- makeIcon(
  iconUrl = "https://image.flaticon.com/icons/svg/138/138310.svg",
  iconWidth = 15, iconHeight = 15,
  iconAnchorX = 22, iconAnchorY = 94,
  shadowUrl = "https://image.flaticon.com/icons/svg/138/138310.svg",
  shadowWidth = 15, shadowHeight = 15,
  shadowAnchorX = 4, shadowAnchorY = 62
)

leaflet(data = food.10) %>%
addTiles() %>%
  addPopups(~long, ~lat, ~ content,
            options = popupOptions(closeButton = FALSE))%>%
  addMarkers(~long, ~lat, icon = Icon, popup = ~content, label = ~as.character(VioCount))
# %>% addProviderTiles(providers$Stamen.Toner)
# %>% addProviderTiles(providers$CartoDB.Positron)
# %>% addProviderTiles(providers$Esri.NatGeoWorldMap)
```

## Top 50 Food Courts in MA with the Most Violations
```{r, warning = FALSE}
food.50 <- food[1:50,]
content <- paste(sep = "<br/>",
                 food.50$businessName,
                 food.50$Address,
                 food.50$CITY,
                 food.50$VioCount
)

Icon <- makeIcon(
  iconUrl = "https://image.flaticon.com/icons/svg/138/138310.svg",
  iconWidth = 15, iconHeight = 15,
  iconAnchorX = 22, iconAnchorY = 94,
  shadowUrl = "https://image.flaticon.com/icons/svg/138/138310.svg",
  shadowWidth = 15, shadowHeight = 15,
  shadowAnchorX = 4, shadowAnchorY = 62
)

leaflet(data = food.50) %>%
addTiles() %>%
  addMarkers(~long, ~lat, icon = Icon, popup = ~content, label = ~as.character(VioCount)) %>%
  addProviderTiles(providers$Stamen.Toner)
# %>% addProviderTiles(providers$CartoDB.Positron)
# %>% addProviderTiles(providers$Esri.NatGeoWorldMap)
```


\dontrun{
# We can't use google api
boston_map <- make_bbox(lat = lat, lon = long, data = food.50)
boston_map <- get_map(location = boston_map, source = "google", maptype = "hybrid")
ggmap(boston_map) +
geom_point(data = food.50, mapping = aes(x = long, y = lat, size = VioCount, color = "red")) +
guides(color = FALSE) +  
  geom_label_repel(
  aes(x = long, y = lat, label = businessName),
  data = food.50,
  family = "Times",
  size = 2,
  box.padding = 0.08, point.padding = 0.1,
  segment.color = "grey50")
}

## First 500 rows of Food Courts in MA with Violations in 2018
```{r, warning = FALSE}
# content <- paste(sep = "<br/>",
# foodcourt_2018$businessName,
# foodcourt_2018$Address)

boston.500 <- foodcourt_2018[1:500, ]

getColor <- function(foodcourt_2018) {
  sapply(foodcourt_2018$count, function(count) {
    if (count >= 10 & count < 20) {
      "orange"
    } else if (count < 10 & count >= 1) {
      "green"
    } else if (count >= 20 & count < 100) {
      "purple"
    } else if (count >= 100 & count < 234) {
      "red"
    }
  })
}

icons <- awesomeIcons(
  icon = "coffee",
  iconColor = "white",
  library = "ion",
  markerColor = getColor(boston.500)
)

# Show first 500 rows from the foodcourt_2018 dataset
leaflet(boston.500) %>%
  addTiles() %>%
  addAwesomeMarkers(~long, ~lat, icon = icons, popup = ~as.character(businessName), options = popupOptions(closeButton = FALSE), label = ~as.character(count)) %>%
  addLegend("bottomright", colors = c("green", "orange", "purple", "red"), labels = c("<10", "10~20", "20~100", ">100"), title = "Violation Counts", opacity = 1) %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>%
  addLayersControl(
    overlayGroups = (foodcourt_2018$ViolLevel),
    options = layersControlOptions(collapsed = FALSE)) %>% 
  addProviderTiles(providers$Esri.NatGeoWorldMap)
# %>% addProviderTiles(providers$Stamen.Toner)
# %>% addProviderTiles(providers$CartoDB.Positron)
```


\dontrun{
boston_map <- make_bbox(lat = lat, lon = long, data = foodcourt_2018)
boston_map <- get_map(location = boston_map)
severe <- filter(foodcourt_2018, count > 80)

ggmap(boston_map) + 
  geom_point(data = severe, mapping = aes(x = long, y = lat, color = count), size = 3) +
  scale_colour_gradient(low = "yellow", high = "red") + 
  geom_label_repel(
    aes(x = long, y = lat, label = businessName),
    data = severe,
    family = "Times",
    size = 2,
    box.padding = 0.08,
    point.padding = 0.1,
    segment.color = "grey50") + 
  ggtitle("Violation counts over 80")
}
